Resource Buying Games

### 2017-04-07 paper.tex
removed todos
polished

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage{todo}
\usepackage{amsmath}
\usepackage[framed]{ntheorem}
\usepackage[style=numeric]{biblatex}

@@

\input{tikz/settings}
\maketitle
\section{Introduction}
In this paper we examine a certain class of games based on congestion models.
Intuitively speaking we consider a set of resources and actors with individual
demands on this set of resources. We model this competing behaviour of actors
in terms of strategic games which are applicable for analysis in regards of
Nash equilibria. Mainly, we are interested in the existence and computability
of pure Nash equilibria (PNE), i.e. a state where each actor has no interest
to uniliterally change her/his behaviour if all other players stick to their
strategy. We examine congestion models with different cost functions of
resource, different structures of resources each player wants to be available
and different demand of players on her/his resources. As main results we prove
the existence of PNE for
\begin{itemize}
  \item matroid games with marginally non-increasing cost functions
  \item congestion games with marginally non-decreasing cost functions
\end{itemize}
In terms of complexity we present an algorithm to compute a PNE for unweighted
(i.e. uniform demands for all players) matroid games with marginally
non-increasing cost functions. Additionally, we construct for non-matroid
structures congestion games with marginally non-increasing cost functions which
specifically do not allow for PNEs. This paper only presents results and
arguments from \cite{main}. Specifically we focus on intuitions and thus
present proofs not in exhaustive detail but try to conway the central ideas.

We start with defining an appropiate congestion model and an associated
strategic game as well as introducing matroids as combinatorial structure
to model desired configurations of resources for players. Following an
algorithm to compute PNEs in unweighted matroid games with marginally
non-increasing cost functions as well as its correctness proof is presented.
Afterwards weighted matroid games with different cost functions are examined
and concludingly, we study non-matroid configuration spaces.

\section{Congestion Model}
In this section we want to introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{R}_{+}$ for
every resource $e\in E$. As an example consider different actors that build a
shared network infrastructure. The connections in the network are resources,
the actors are the players which have individual spots they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
  \item we call $c_{e}$ \emph{marginally non-increasing} if
    $c_{e}(y + \delta) - c_{e}(y) \leq c_{e}(x + \delta) - c_{e}(x)$ holds
    for all $x,y,\delta\in N$ with $x\leq y$
  \item analogously $c_{e}$ is \emph{marginally non-decreasing} if
    $c_{e}(y + \delta) - c_{e}(y) \geq c_{e}(x + \delta) - c_{e}(x)$ holds
    for all $x,y,\delta\in N$ with $x\leq y$
\end{itemize}
Note that linear and constant cost functions are marginally non-increasing.

@@

players. To model this we consider the resource buying game 

@@

where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
$\mathcal{P}_{i} = \mathbb{R}_{+}^{|E|}$ to model how much every player
contributes in paying for the cost of every resource. We denote the element
from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$ and call $e\in E$ bought
under $\tupel{S, p}\in \mathcal{S}\times\mathcal{P}$ if
$c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The function $\pi$ gives the payoff for
every player for a strategy profile $\tupel{S, p}$ by

@@

Thus, every player tries to minimise her personal contribution to the costs

@@

Matroids can be defined as a ground-set and the family of linear

@@

  \item the empty set is linear independent,
  \item all subset of a linear independent set are linear independent and
  \item for two linear independent sets we can find an element of the larger
    set that forms a linear independent set when added to the smaller set.

@@

We use an equivalent definition of matroids which in a way captures the idea of

@@

by iteratively adding edges which do not close a cycle: every added edge works
towards a basis in $\mathcal{S}$ and opens a dimensionality by connecting

@@

  the matroid $\tupel{E\setminus\set{e}, \set{C\subseteq

@@

e.g. deletion of an edge in the spanning tree matroid which is a bridge yields
an empty set of bases and thus no valid matroid. Analogously, any set of edges
that, when removed, disconnect the graph contains at least one element
necessarily present in any basis. We call such sets cuts\footnote{see Figure
\ref{fig:cuts} for an illustration} and define them as follows.

@@

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game builds upon a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing.

@@

the elements which are chosen for her up to the current state

@@

added load causes and how much load already is placed upon the
resource(\emph{current load}). Initially for every resource $e$ the current
load is zero and the next load causes $c_{e}(1)$ cost. We can devide the

@@

          \item all player: delete elements $C\setminus\set{e}$ from matroid

@@

          \item exists player with incomplete basis: goto (ii)

@@

    For a more detailed pseudo-code representation and an description of how to
    compute the minimal cut and the minimal cost element within we refer to
    \cite[Algorithm 1 and 3.3 A Subroutine to Detect $C^{\ast}, e^{\ast}$ and
    $i^{\ast}$]{main}.}

@@

By induction on the iterations one can prove that the cost of the chosen
element in step (ii) always decreases. This is a key lemma to prove the
correctness of the algorithm. Because, if we assume to have a beneficial
alternative to the computed basis for one player there is an element with
less cost. This alternative element is not part of the selected cut since
it would be removed for all players and thus keep its marginal cost although
only elements with higher costs are removed (by choice of the element in the
cut). Furthermore, the alternative element cannot be available to the player
for which the cut is selected since both elements open the
\enquote{same dimensionality} in contradiction to choosing a cut. Thus, the
alternative element has been removed before which implies less cost in a
previous step to the iteration where the original element was chosen. This
contradicts the monotonicity of costs of considered elements through the
iterations. Thus

@@

\section{Weighted Matroid Games}
Starting from a congestion model where every player aims to buy a basis from
a certain matroid and every player puts an individual demand upon the resources
she/he uses we derive a complete characterisation of PNEs as well as show that
every socially optimal solution actually induces a PNE. Firstly, we give some
auxiliary definitions (with a profile $B\in\mathcal{B}$, a resource $e\in E$):
\begin{itemize}
  \item $N_{e}(B) = \set{i\in N\middle| e\in B_{i}}$ is the set of players
    which use resource $e$ in the profile $B$
  \item $\ex_{i}(e) = \set{f\in E\setminus\set{e}\middle|
    (B_{i}\setminus\set{e})\cup\set{f}\in\mathcal{B}_{i}}$ is the set of
    resources player $i\in N_{e}(B)$ could exchange $e$ with
  \item $F$ is the set of resources that is obligatory for any player, i.e.
    every element of $F$ is present in \emph{all} bases of one (or more) player
  \item $\Delta_{i}\tupel{B;e\rightarrow f}$ is the marginal cost player $i$
    has to pay for resource $f$ if he intends to use $f$ instead of $e$
    (we define the minimum over all resources $e$ can be exchanged with as
    $\Delta_{i}^{e}(B) = \min_{f\in\ex_{i}(e)}\Delta_{i}(B;e\rightarrow f)$)
\end{itemize}
With these definitions we can formulate the following characterisation of
PNEs which holds for all non-negative and non-decreasing cost functions.
\begin{theo}
  For a weighted matroid resource buying game $\tupel{N, E, \mathcal{B}, d, c}$
  there is a payment vector $p$ s.t. $\tupel{B\in\mathcal{B}, p}$ is a PNE
  if and only if
  \begin{equation*}
    c_{e}(B)\leq\sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B) \text{ for all } e\in
    E\setminus F
  \end{equation*}
\end{theo}
The \enquote{only if} direction is easily given by the fact that the cost
of a resource is the sum of the contributions of every player for this resource
and no player has an incentive to uniliterally change to another basis of
her/his matroid. While, for the \enquote{if} direction, we let for elements in
$F$ one player for whom this resource is obligatory pay for this resource
(since she/he needs this resource to be available she/he can not choose to
uniliterally change her/his payment). For all other elements we can define the
payments as follows:
\begin{equation*}
  p_{i}^{e} = \begin{cases}
    0 &\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) = 0\\
    \underbrace{
      \frac{c_{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}
    }_{\leq 1}\cdot\Delta_{i}^{e}(B) &\text{ otherwise}
  \end{cases}
\end{equation*}
which yields $p_{i}^{e}\leq \Delta_{i}^{e}$ for all $e\in E\setminus F$
implying a PNE.

Using this one can derive a series of inequalities to show that every socially
optimal solution satisfies the given characterisation and hence
\begin{theo}
  Every weighted matroid resource buying game with marginally non-increasing
  cost functions posses a PNE.
\end{theo}
For completeness we state - without going into details - an analogous result
for non-decreasing cost functions. Again starting from a socially optimal
configuration one can derive a pricing vector (called marginal cost pricing)
which forms with the given configuration a PNE. Especially this result is
also viable for non-matroid strategy spaces, yielding:
\begin{theo}
  Let $G$ be a weighted resource buying game with non-decreasing marginal costs
  and let $S^{\ast}$ be a socially optimal solution. Then, marginal cost
  pricing induces a PNE.
\end{theo}

@@

Finally, we consider in this section non-matroid strategy spaces. Specifically,
we present a construction which illustrates how to obtain a weighted two player

@@

  For every non-matroid anti-chain $\mathcal{S}$ on a set of resources $E$,
  there exists a weighted two-player resource buying game
  $G = \tupel{\tilde{E},

@@

  so that $G$ does not posses a PNE.

@@

As said before we start with an anti-chain $\mathcal{S}\subseteq 2^{E}$ which

@@

Especially we can guarantee that there are two elements in $\mathcal{S}$ s.t.

@@

$X_{i}, Y_{i}\in\mathcal{S}_{i}$ for $i = 1,2$ as described above. We interleaf
the ground-sets of $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ by precisely three
elements $x,y,z$ which we identify in both copies differently. Namely, we set
$x = a_{1} = b_{2}$, $y = b_{1} = a_{2}$, and $z = c_{1} = c_{2}$. The set of
resources for $G$ is now the union of both ground-sets w.r.t. the intersection
which is $\set{x,y,z}$. Furthermore we fix the cost functions of all elements
in $\tilde{E}\setminus(X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2})$ to a high constant
$M$ which ensures that both players only play within $X_{i}, Y_{i}$ (for
$i = 1,2$ respectively). In this \enquote{sub-arena} we set the cost functions
of all elements other than $\set{x,y,z}$ to $0$ regardless of the demand. And
concludingly we set $c_{x}(t) = t$, $c_{y}(t) = 5\frac{1}{2}$, and
$c_{z}(t) = 4$ and an individual demand of the players of $d_{1} = 5$ and

@@

By examining the restricted environment of the cost inducing elements ($x,y,z$)
and the conclusion that one player either only contributes to $x$ or $y$ and
$z$ and the other only to $y$ or $x$ and $z$ one can conclude that neither
$x\in Z_{1}^{\ast}$ nor $x\notin Z_{1}^{\ast}$ which yields a contradiction to
the existence of a PNE and thus concludes the argument on the section-leading
theorem.

\section{Conclusion}
Among other restrictions we studied unweighted congestion games with marginally
non-increasing cost functions. For these games matroids are precisely the
configuration spaces to guarantee PNEs as well as allow for efficient
computation of one PNE. For weighted matroid games with marginally
non-increasing cost functions the existence of PNEs can be assured. Also for
weighted congestion games with marginally non-decreasing cost functions PNEs
are given. Hereby the structure of strategy spaces is unrestricted.
Concludingly, marginally non-increasing cost functions demand matroid strategy
spaces as combinatorial structure which capture e.g. spanning trees, linear
independence, \dots. On the other hand marginally non-decreasing cost functions
might induce a certain stability in a market by ensuring the existence of PNEs.

>>>>

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage[hide]{todo}
\usepackage{amsmath}
\usepackage[framed]{ntheorem}
\usepackage[style=numeric]{biblatex}

@@

\input{tikz/settings}
\maketitle
\section{Introduction}
In this paper we examine a certain class of games based on congestion models.
Intuitively speaking, we consider a set of resources and actors with individual
demands on this set of resources. We model this competing behaviour of actors
in terms of strategic games which are applicable for analysis regarding
Nash equilibria. Mainly, we are interested in the existence and computability
of pure Nash equilibria (PNE), i.e. a state where each actor has no interest
to unilaterally change her/his behaviour if all other players stick to their
strategy. We examine congestion models with different cost functions for
resources, different structures of resources each player wants to be available
and different demand of players on her/his resources. As main results we prove
the existence of PNE for
\begin{itemize}
  \item matroid games with marginally non-increasing cost functions
  \item congestion games with marginally non-decreasing cost functions
\end{itemize}
In terms of complexity we present an algorithm to compute a PNE for unweighted
(i.e. uniform demands for all players) matroid games with marginally
non-increasing cost functions. Additionally, we construct congestion games for
non-matroid structures with marginally non-increasing cost functions which
specifically do not allow for PNEs. This paper only presents results and
arguments from \cite{main}. Specifically, we focus on intuitions and thus
present proofs not in exhaustive detail but try to convey the central ideas.

We start by defining an appropiate congestion model and an associated
strategic game as well as by introducing matroids as combinatorial structures
to model desired configurations of resources for players. Following we present
an algorithm to compute PNEs in unweighted matroid games with marginally
non-increasing cost functions and its correctness proof.
Afterwards, we examine weighted matroid games with different cost functions
and concludingly, we study non-matroid configuration spaces.

\section{Congestion Model}
In this section, we introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as a family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{R}_{+}$ for
every resource $e\in E$. As an example, consider different actors that build a
shared network infrastructure. The connections in the network are resources,
the actors are the players which have individual nodes they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly, we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell_{e}(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
  \item we call $c_{e}$ \emph{marginally non-increasing} if
    $c_{e}(y + \delta) - c_{e}(y) \leq c_{e}(x + \delta) - c_{e}(x)$ holds
    for all $x,y,\delta\in N$ with $x\leq y$
  \item analogously $c_{e}$ is \emph{marginally non-decreasing} if
    $c_{e}(y + \delta) - c_{e}(y) \geq c_{e}(x + \delta) - c_{e}(x)$ holds
    for all $x,y,\delta\in N$ with $x\leq y$
\end{itemize}
Note that linear and constant cost functions are marginally non-increasing.

@@

players. This leads to a definition of resource buying game:
  For a congestion model $\mathcal{M} = \tupel{N, E, \mathcal{S},
  \tupel{d_{i}}_{i\in N}, \tupel{c_{e}}_{e\in E}}$ we define a
  \emph{resource buying game}

@@

  with $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
  $\mathcal{P}_{i} = \mathbb{R}_{+}^{|E|}$ (which is the contribution of each
  player to buy the demanded strategy profile).
  We denote the element from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$
  and call $e\in E$ \emph{bought} under $\tupel{S, p}\in
  \mathcal{S}\times\mathcal{P}$ if $c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The
  function $\pi$ defines the payoff for every player for a strategy profile
  $\tupel{S, p}$ by

@@

Thus, every player tries to minimise her/his personal contribution to the costs

@@

Matroids can be defined as a ground-set and the family of linearly

@@

  \item the empty set is linearly independent,
  \item all subsets of a linearly independent set are linearly independent and
  \item for two linearly independent sets we can find an element of the larger
    set that forms a linearly independent set when added to the smaller set.

@@

We use an equivalent definition of matroids which captures the idea of

@@

by iteratively adding edges to a result which do not close a cycle in the
subgraph induced by the edges in the result: every added
edge works towards a basis in $\mathcal{S}$ and opens a dimension by connecting

@@

@@

e.g. deletion of an edge in the graph which is a bridge yields
an empty set of bases in the spanning tree matroid and thus no valid matroid.
Analogously, any set of edges that, when removed, disconnects the graph
contains at least one element necessarily present in any basis. We call such
sets cuts\footnote{see Figure \ref{fig:cuts} for an illustration} and define
them as follows.  \begin{defi}

@@

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game is based on a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing.

@@

the elements which are chosen for her/him up to the current state

@@

added load causes and how much load already is placed on the resource
(\emph{current load}). Initially, for every resource $e$ the current
load is zero and the next load causes $c_{e}(1)$ cost. We can divide the

@@

            \item all players: delete elements $C\setminus\set{e}$ from matroid

@@

            \item if exists player with incomplete basis: goto (ii)

@@

    For a more detailed pseudo-code representation and a description of how to
    compute the minimal cut and the minimal cost element in this cut we refer
    to \cite[Algorithm 1 and 3.3 A Subroutine to Detect $C^{\ast}, e^{\ast}$
    and $i^{\ast}$]{main}.}

@@

By induction on the number of iterations we can prove that the cost of the
chosen element in step (ii) always decreases. This is a key insight to prove
the correctness of the algorithm. Because, if we assume to have a beneficial
alternative to the computed basis for one player there must exist an element
with less cost. This alternative element cannot be part of the selected cut
since it would be removed for all players and thus keep its marginal cost
although only elements with higher costs are removed (by choice of the element
in the cut). Furthermore, the alternative element cannot be available to the
player for which the cut is selected since both elements open the
\enquote{same dimension} in contradiction to the choice of a cut. Thus, the
alternative element must already have been removed which implies less
cost in a previous step to the iteration where the original element was chosen.
This contradicts the monotonicity of costs of considered elements through the
iterations. {Thus, we get the following theorem:

@@

}

\section{Weighted Matroid Games}
Starting from a congestion model where every player aims to buy a basis of
a certain matroid and every player puts an individual demand upon the resources
she/he uses we derive a complete characterisation of PNEs as well as show that
every socially optimal solution induces a PNE. First of all, we give some
auxiliary definitions (with a profile $B\in\mathcal{B}$, a resource $e\in E$):
\begin{itemize}
  \item $N_{e}(B) = \set{i\in N\middle| e\in B_{i}}$ is the set of players
    which use resource $e$ in the profile $B$
  \item $\ex_{i}(e) = \set{f\in E\setminus\set{e}\middle|
    (B_{i}\setminus\set{e})\cup\set{f}\in\mathcal{B}_{i}}$ is the set of
    resources player $i\in N_{e}(B)$ could exchange $e$ with
  \item $F$ is the set of resources that is obligatory for any player, i.e.
    every element of $F$ is present in \emph{all} bases of one (or more) player
  \item $\Delta_{i}\tupel{B;e\rightarrow f}$ is the marginal cost player $i$
    has to pay for resource $f$ if he intends to use $f$ instead of $e$.
    We define the minimum over all resources $e$ can be exchanged with as
    $\Delta_{i}^{e}(B) = \min_{f\in\ex_{i}(e)}\Delta_{i}(B;e\rightarrow f)$
\end{itemize}
With these definitions we can formulate the following characterisation of
PNEs which holds for all non-negative and non-decreasing cost functions.
\begin{theo}
  For a weighted matroid resource buying game $\tupel{N, E, \mathcal{B}, d, c}$
  there is a payment vector $p$ s.t. $\tupel{B\in\mathcal{B}, p}$ is a PNE
  if and only if
  \begin{equation*}
    c_{e}(B)\leq\sum_{i\in N_{e}(B)}\Delta_{i}^{e}(B) \text{ for all } e\in
    E\setminus F
  \end{equation*}
\end{theo}
The \enquote{only if} direction is easily shown by the fact that the cost
of a resource equals the sum of the contributions of every player for this
resource and no player has an incentive to unilaterally change to another basis
of her/his matroid. While, for the \enquote{if} direction, we let for elements
in $F$ one player for whom this resource is obligatory pay for this resource
(since she/he needs this resource to be available she/he can not choose to
unilaterally change her/his payment). For all other elements we can define the
payments as follows:
\begin{equation*}
  p_{i}^{e} = \begin{cases}
    0 &\text{ if } \sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B) = 0\\
    \underbrace{
      \frac{c_{e}(B)}{\sum_{j\in N_{e}(B)}\Delta_{j}^{e}(B)}
    }_{\leq 1}\cdot\Delta_{i}^{e}(B) &\text{ otherwise}
  \end{cases}
\end{equation*}
which yields $p_{i}^{e}\leq \Delta_{i}^{e}$ for all $e\in E\setminus F$
implying a PNE.

Using this we can derive a series of inequalities to show that every socially
optimal solution satisfies the given characterisation and hence:
\begin{theo}
  Every weighted matroid resource buying game with marginally non-increasing
  cost functions possesses a PNE.
\end{theo}
For completeness we state - without going into details - an analogous result
for non-decreasing cost functions. Again starting from a socially optimal
configuration we can derive a pricing vector (called marginal cost pricing)
which forms a PNE with the given configuration. Noteably, this result is
also true for non-matroid strategy spaces, yielding:
\begin{theo}
  Let $G$ be a weighted resource buying game with non-decreasing marginal costs
  and let $S^{\ast}$ be a socially optimal solution. Then, marginal cost
  pricing induces a PNE.
\end{theo}

@@

Finally, we consider non-matroid strategy spaces. Specifically,
we present a construction to obtain a weighted two player

@@

  For every non-matroid anti-chain $\mathcal{S}$ (i.e. a family of sets which
  are not ordered by $\subseteq$) on a set of resources $E$, there exists a
  weighted two-player resource buying game $G = \tupel{\tilde{E},

@@

  so that $G$ does not possess a PNE.

@@

We start with an anti-chain $\mathcal{S}\subseteq 2^{E}$ which

@@

Especially, we can guarantee that there are two elements in $\mathcal{S}$ s.t.

@@

$X_{i}, Y_{i}\in\mathcal{S}_{i}$ for $i = 1,2$ as described above. We
interleave the ground-sets of $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ by
precisely three elements $x,y,z$ which we identify differently in both copies.
Namely, we set $x = a_{1} = b_{2}$, $y = b_{1} = a_{2}$, and
$z = c_{1} = c_{2}$. The set of resources for $G$ is now the union of both
ground-sets w.r.t. their intersection which is $\set{x,y,z}$. Furthermore, we
fix the cost functions of all elements in
$\tilde{E}\setminus(X_{1}\cup X_{2}\cup Y_{1}\cup Y_{2})$ to a high constant
$M$ which ensures that both players only play within $X_{i},
Y_{i}$ (for $i = 1,2$ respectively). In this \enquote{sub-arena} we set the
cost functions of all elements other than $\set{x,y,z}$ to $0$ regardless of
the demand. And concludingly, we set $c_{x}(t) = t$, $c_{y}(t) = 5\frac{1}{2}$,
and $c_{z}(t) = 4$ and an individual demand of the players of $d_{1} = 5$ and

@@

By examining the restricted environment of the cost inducing elements
$\set{x,y,z}$ and the conclusion that one player either only contributes to $x$
or $y$ and $z$ and the other only to $y$ or $x$ and $z$ one can conclude that
neither $x\in Z_{1}^{\ast}$ nor $x\notin Z_{1}^{\ast}$ which yields a
contradiction to the existence of a PNE and concludes the argument on the
theorem proposed at the beginning of the section.

\section{Conclusion}
Among other restrictions we studied unweighted congestion games with marginally
non-increasing cost functions. For these games matroids are precisely the
configuration spaces to guarantee PNEs as well as allow for efficient
computation of one PNE. For weighted matroid games with marginally
non-increasing cost functions the existence of PNEs can be assured as well as
for weighted congestion games with marginally non-decreasing cost functions.
Hereby the structure of strategy spaces is unrestricted.
Concludingly, marginally non-increasing cost functions demand matroid strategy
spaces as combinatorial structures which capture e.g. spanning trees, linear
independence, etc. On the other hand, marginally non-decreasing cost functions
might induce a certain stability in a market by ensuring the existence of PNEs.
